Division and Factorization of p-Adic Polynomials

### 2016-01-30 polynomials/muldivfact.tex
Numerical experimentation for slope factorization
Numerical results added to the article for slope factorization.
Sage implementation is given.

>>>>

{\bf Numerical experimentations.} We have implemented the following scheme to illustrate the behaviour of precision
for slope factorization over $\mathbb{Q}_2 [X].$
We start with random polynomials $A$ and $B$ with given minoration on their Newton polygons, assuring
they have no common slope.
We compute $P=AB$ and then $A^{(1)}$, and compare the obtained precision on $A^{(1)}$
(jagged) with the estimation given using $\Psi_{A^{(1)}}$ and Proposition \ref{prop:precA1}
assuming~\textbf{(H)}. The mean amount of lost digits for $1000$ experiments is given in the following array.
Two settings are possible for the initial $A$ and $B$ : relative or absolute precision equal to $100$ for their coefficients.

{\small%
\noindent \hfill%
\renewcommand{\arraystretch}{1.2}%
\begin{tabular}{|c|c|c|c|c|}%
\hline
\multirow{2}{*}{Polynomials} & 
\multirow{2}{*}{\hspace{2mm}Precision\hspace{2mm}} & 
\multicolumn{3}{c|}{Gain of precision} \\
\cline{3-5}
& &Jagged & Newton
      & \raisebox{-0.5mm}{Lattice} \\
\hline
\multirow{2}{*}{
\begin{tikzpicture}[xscale=0.1, yscale=0.05]
\draw[->] (0,-.5) -- (0,10.5);
\draw[->] (-0.05,0) -- (13.5,0);
\draw (6,-.75) -- (6,.75);
\node[below, right] at (6,-2) {$d$};
\draw (0,5) -- (2,-2) -- (6,0) -- (10,3) -- (13,10);
\draw[dotted] (6,0) -- (6,10);
\node at (3,5) {$A$};
\node at (9,5) {$B$};
\end{tikzpicture}}
& abs & $-14.5$ & $-14.7$ & $0$ \\
& rel & $-1.5$ & $-3.6$ & $0$ \\
\hline
\multirow{2}{*}{\begin{tikzpicture}[xscale=0.11, yscale=0.05]
\draw[->] (0,-.5) -- (0,10.5);
\draw[->] (-0.05,0) -- (13.5,0);
\draw (3,-.75) -- (3,.75);
\node[below, left] at (3,-2.5) {$d$};
\draw (0,5) -- (2,1) -- (3,0) -- (8,-2) -- (10,10);
\draw[dotted] (3,0) -- (3,10);
\node at (1.5,5) {$A$};
\node at (6.5,5) {$B$};
\end{tikzpicture}}
& abs & $0$ & $0$ & $0$ \\
& rel & $-0.3$ & $-1.2$ & $0$ \\
\hline
\end{tabular}
\hfill \null}
